Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-12 paper/structureScene.tex
mitigating floating figures issue
fix figs
review beginning of section VI

@@

%For most of the experiments reported in this paper, we will consider the DCASE2013 dataset \cite{giannoulis2013database, 7100934}. Larger datasets exists: the
%Rouen dataset \cite{rakotomamonjy2015histogram} and the public part of the DCASE2016 challenge.%

In the experiments reported in this paper, we consider the DCASE 2013 \cite{giannoulis2013database, 7100934} and the public part of the DCASE 2016 datasets  \cite{Mesaros2016_EUSIPCO}.

The DCASE 2013 dataset consists of two parts, namely a public and a private subset, each made up of $100$ $30$-second recordings of various acoustic scenes. The $100$ recordings are evenly divided into $10$ acoustic scene classes. To build the DCASE 2013 dataset, three different recordists visited a wide variety of locations in Greater London over a period of several months and in each scene recorded a few minutes of audio. No
systematic variations in the recordings covaried with scene
type: all recordings were made under moderate weather conditions, at varying times of day and week, and each recordist recorded each scene type. As a consequence, DCASE2013 dataset has interesting intra-class diversity while remaining manageable in terms of size, making it suitable for extensive evaluation of algorithmic design choices \cite{lagrange:hal-01082501}.

In addition, it is still a challenging dataset, with a state-of-the-art system based on feature design and SVMs achieving $76\%$ \cite{roma2013} (winner of the DCASE2013 challenge), while recent approaches based on label tree embedding achieves between $84\%$ and $87\%$ on DCASE 2013 depending on the prior knowledge used during training \cite{phan2016label}.

@@

@@

\begin{figure}
\begin{center}
\includegraphics[width=8cm]{gfx/unsupervised_test2}
\caption{ASSR: $p@k$ obtained for MFCCs and scattering with logarithmic compression.}
\label{fig:ASS_1}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=8cm]{gfx/unsupervised_test1}
\caption{ASSR: $p@k$ obtained for scattering with and without logarithmic compression.}
\label{fig:ASS_2}
\end{center}
\end{figure}

@@

>>>>

%\renewcommand{\baselinestretch}{2}

@@

%For most of the experiments reported in this paper, we will consider the DCASE2013 dataset \cite{giannoulis2013database, 7100934}. Larger datasets exists: the
%Rouen dataset \cite{rakotomamonjy2015histogram} and the public part of the DCASE2016 challenge.%
The experiments in this paper are carried out on the private part of the DCASE 2013 dataset\cite{giannoulis2013database, 7100934} and the public part of the DCASE 2016 dataset \cite{Mesaros2016_EUSIPCO}.

The DCASE 2013 dataset consists of two parts, namely a public and a private subset, each made up of $100$ $30$-second recordings of various acoustic scenes. The $100$ recordings are evenly divided into $10$ acoustic scene classes. To build the DCASE 2013 dataset, three different recordists visited a wide variety of locations in Greater London over a period of several months and in each scene recorded a few minutes of audio. No
systematic variations in the recordings covaried with scene
type: all recordings were made under moderate weather conditions, at varying times of day and week, and each recordist recorded each scene type. As a consequence, DCASE2013 dataset enjoys an interesting intra-class diversity while remaining manageable in terms of size, making it suitable for extensive evaluation of algorithmic design choices \cite{lagrange:hal-01082501}.

In addition, it is still a challenging dataset, with a state-of-the-art system based on feature design and SVMs achieving $76\%$ \cite{roma2013} (winner of the DCASE2013 challenge), while recent approaches based on label tree embedding achieve between $84\%$ and $87\%$ on DCASE 2013 depending on the prior knowledge used during training \cite{phan2016label}.

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=\columnwidth]{gfx/unsupervised_test2}
\caption{ASSR: $p@k$ obtained for MFCCs and scattering with logarithmic compression.}
\label{fig:ASS_1}
\end{center}
\end{figure}

@@

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=\columnwidth]{gfx/unsupervised_test1}
\caption{ASSR: $p@k$ obtained for scattering with and without logarithmic compression.}
\label{fig:ASS_2}
\end{center}
\end{figure}
